---
title: Forecast reconciliation
subtitle: A brief overview
author: Rob J Hyndman
pdf-engine: latexmk
fig-width: 9
fig-height: 4.5
format:
  beamer:
    theme: monash
    aspectratio: 169
    fontsize: 14pt
    section-titles: false
    knitr:
      opts_chunk:
        dev: "CairoPDF"
include-in-header: header.tex
cite-method: biblatex
bibliography: hts.bib
biblio-title: References
highlight-style: tango
keep-tex: true
execute:
  echo: false
  message: false
  warning: false
  cache: true
---

```{r}
#| cache: false
source("setup.R")
```

## Forthcoming paper

\placefig{0}{1.1}{height=8.3cm, width=20cm}{IJFcover}

\begin{textblock}{9.2}(6.3, 1.2)\fontsize{13}{14}\sf
\begin{itemize}\parskip=0.1cm
\item Athanasopoulos, Hyndman, Kourentzes, Panagiotelis (2024)
\emph{International~Journal~of~Forecasting},
``Forecast reconciliation: A review''.
\item Preprint at \texttt{\href{https://robjhyndman.com/frreview}{robjhyndman.com/frreview}}
\end{itemize}
\end{textblock}

\placefig{6.07}{5.}{trim = 0 40 0 0, clip=TRUE, width=10cm, height=4.1cm}{george}
\placefig{9.4}{5.}{trim = 0 40 0 0, clip=TRUE, width=10cm, height=4.1cm}{nikos}
\placefig{12.7}{5.}{trim = 0 0 0 0, clip=TRUE, width=10cm, height=4.1cm}{tas}

## Outline

\vspace*{0.7cm}\tableofcontents

# Australian tourism aggregations

## Australian tourism regions

```{r}
#| label: ausmap
#| fig-height: 3.5
#| fig-width: 12
#| eval: false
library(sf)
# Use Okabe-Ito color-blind friendly color palette
state_colors <- c(
  `New South Wales` = "#56b4e9",
  `Victoria` = "#0072b2",
  `Queensland` = "#009e73",
  `South Australia` = "#f0e442",
  `Northern Territory` = "#d55e00",
  `Western Australia` = "#e69f00",
  `Tasmania` = "#cc79a7",
  `Australian Capital Territory` = "#cccccc"
)

cairo_pdf("./figs/aus_map.pdf", width = 10, height = 6)
read_sf("tourism/Tourism_Regions_2020.shp") |>
  rename(State = "STE_NAME16") |>
  ggplot() +
  geom_sf(aes(fill = State), alpha = 0.8) +
  theme_void() +
  theme(text = ggplot2::element_text(family = 'Fira Sans')) +
  scale_fill_manual(values = state_colors)
crop::dev.off.crop()
```

\placefig{-0.5}{1.2}{height=7.8cm, width=16cm}{aus_map}
\begin{textblock}{6.5}(9.1,1.1)
\begin{block}{}\fontsize{12.2}{14}\sf
  \begin{itemize}\itemsep=0.1cm\parskip=0cm
    \item Monthly data on visitor night from 1998 -- 2017
    \item From \textit{National Visitor Survey}, annual interviews of 120,000 Australians aged 15+
    \item Geographical hierarchy:
    \begin{itemize}
    \item 7 states
    \item 27 zones
    \item 75 regions
    \end{itemize}
  \item Also disaggregated by purpose of travel (business, holiday, visiting, other)
  \end{itemize}
\end{block}
\end{textblock}

## Australian tourism data

```{r}
#| label: tourism_plots
#| fig-width: 12
#| fig-height: 5
p1 <- tourism |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Visitor nights") + xlab("Month") +
  #scale_y_log10() +
  ggtitle("Total domestic travel: Australia")
p2 <- tourism |>
  group_by(state) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Visitor nights") + xlab("Month") +
  scale_y_log10() +
  ggtitle("Total domestic travel: by state") +
  scale_color_manual(
    values =
      c(
        NSW = "#56b4e9",
        VIC = "#0072b2",
        QLD = "#009e73",
        SA = "#f0e442",
        NT = "#d55e00",
        WA = "#e69f00",
        TAS = "#cc79a7",
        ACT = "#cccccc"
      )
  )
p3 <- tourism |>
  filter(state == "NSW") |>
  group_by(zone) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Visitor nights") + xlab("Month") +
  #scale_y_log10() +
  ggtitle("Total domestic travel: NSW by zone")
p4 <- tourism |>
  filter(zone == "South NSW") |>
  group_by(region) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Visitor nights") + xlab("Month") +
  #scale_y_log10() +
  ggtitle("Total domestic travel: South NSW by region")
p5 <- tourism |>
  group_by(purpose) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Visitor nights") + xlab("Month") +
  #scale_y_log10() +
  ggtitle("Total domestic travel: by purpose of travel")
p6 <- tourism |>
  filter(region == "Snowy Mountains") |>
  group_by(purpose) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Visitor nights") + xlab("Month") +
  #scale_y_log10() +
  ggtitle("Total domestic travel: Snowy Mountains by purpose of travel")

aligned_plots <- align_patches(p1, p2, p3, p4, p5, p6)
for (i in seq_along(aligned_plots)) {
  cairo_pdf(paste0("./figs/tourism", i, ".pdf"), width = 12 * .8, height = 5 * .8)
  print(aligned_plots[[i]])
  crop::dev.off.crop()
}

p1_m <- tourism |>
  summarise(visitors = sum(visitors)/1e3) |>
  autoplot(visitors) +
  xlab("Month") + ylab("")
p1_q <- tourism |>
  summarise(visitors = sum(visitors)/1e3) |>
  mutate(Quarter = yearquarter(month)) |>
  index_by(Quarter) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Overnight trips (thousands)") + xlab("Quarter")
p1_y <- tourism |>
  summarise(visitors = sum(visitors)/1e3) |>
  mutate(Year = year(month)) |>
  index_by(Year) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  xlab("Year") + ylab("") +
  ggtitle("Total domestic travel: Australia") +
  xlim(1998,2017.8)


cairo_pdf("./figs/tourism7.pdf", width = 12 * .8, height = 6 * .8)
print(p1_y / p1_q / p1_m)
crop::dev.off.crop()

p1_m <- tourism |>
  filter(zone == "South NSW") |>
  summarise(visitors = sum(visitors)/1e3) |>
  autoplot(visitors) +
  xlab("Month") + ylab("")
p1_q <- tourism |>
  filter(zone == "South NSW") |>
  summarise(visitors = sum(visitors)/1e3) |>
  mutate(Quarter = yearquarter(month)) |>
  index_by(Quarter) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  ylab("Overnight trips (thousands)") + xlab("Quarter")
p1_y <- tourism |>
  filter(zone == "South NSW") |>
  summarise(visitors = sum(visitors)/1e3) |>
  mutate(Year = year(month)) |>
  index_by(Year) |>
  summarise(visitors = sum(visitors)) |>
  autoplot(visitors) +
  xlab("Year") + ylab("") +
  #scale_y_log10() +
  ggtitle("Total domestic travel: South NSW") +
  xlim(1998,2017.8)

cairo_pdf("./figs/tourism8.pdf", width = 12 * .8, height = 6 * .8)
print(p1_y / p1_q / p1_m)
crop::dev.off.crop()
```

\only<1>{\placefig{0.1}{1.4}{width=15.8cm}{tourism1}}
\only<2>{\placefig{0.1}{1.4}{width=15.8cm}{tourism2}}
\only<3>{\placefig{0.1}{1.4}{width=15.8cm}{tourism3}}
\only<4>{\placefig{0.1}{1.4}{width=15.8cm}{tourism4}}
\only<5>{\placefig{0.1}{1.3}{width=15.8cm}{tourism5}}
\only<6>{\placefig{0.1}{1.3}{width=15.8cm}{tourism6}}

## Australian tourism data

\begin{textblock}{6}(0.2,1.2)
\centering\fontsize{12}{13}\sf
\textbf{Geographical division}\\
\includegraphics[width = 5.5cm, trim= 0 0 180 0, clip=true]{aus_map}\\[-0.4cm]
\faTimes\\
\textbf{Purpose of travel}\\
{\fontsize{11}{12}\sf Holiday, Visiting friends \& relatives, Business, Other}
\end{textblock}

\begin{textblock}{10}(6.1,1)
\fontsize{11}{14}\sf\tabcolsep=0.12cm
\begin{itemize}
\item \textbf{Grouped ts}\newline (geographical divisions $\times$ purpose of travel)

\begin{tabular}{lccccc}
\toprule
  & \textbf{AUS} & \textbf{States} & \textbf{Zones$^\ast$} & \textbf{Regions} & \textbf{Tot}\\
  \midrule
  \textbf{geographical} & {\color{newblue}1} & {\color{newblue}7} & {\color{newblue}21} & {\color{newblue}76} & 105 \\
  \textbf{purpose} & {\color{newblue}4} & {\color{newblue}28} & {\color{newblue}84} & {\color{avocado}304} & 420\\
  \midrule
  \textbf{total} & 5 & 35 & 105 & 380 & \textbf{525}\\
  \bottomrule
\end{tabular}
\centerline{{\color{newblue}$n_a = 221$}, {\color{avocado}$n_b = 304$}, and $\textbf{n = 525}$}

\end{itemize}
\end{textblock}


# Optimal forecast reconciliation

## Linearly constrained time series

\begin{textblock}{8.8}(0.2,1.5)
Almost all collections of time series with linear constraints can be written \rlap{as}
\centerline{\colorbox[RGB]{210,210,210}{$\bY_{t}=\color{blue}\bS\color{red}\bm{b}_{t}$}}
\vspace*{-0.9cm}\begin{itemize}\parskip=0cm\itemsep=0cm
\item $\by_t=$ vector of all series at time $t$
\item $ y_{\text{Total},t}= $ aggregate of all series at time
$t$.
\item $ y_{X,t}= $ value of series $X$ at time $t$.
\item $\color{red}{\bm{b}_t}=$ vector of most disaggregated series at time $t$
\item $\color{blue}{\bS}=$ ``structural matrix'' containing the linear constraints.
\end{itemize}
\end{textblock}

\begin{textblock}{5.7}(11.4,0.1)
\begin{minipage}{4cm}
\begin{block}{}\centering
\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,draw,fill=red!15,inner sep=2pt]
\tikzstyle[level distance=.3cm]
\tikzstyle[sibling distance=12cm]
\tikzstyle{level 1}=[sibling distance=10mm,font=\small,set style={{every node}+=[fill=blue!15]}]
\node{Total}[edge from parent fork down]
 child {node {A}
 }
 child {node {B}
 }
 child {node {C}
 };
\end{tikzpicture}
\end{block}
\end{minipage}
\end{textblock}

\begin{textblock}{5.7}(9.4,2.8)\fontsize{14}{15}\sf
\begin{align*}
\bY_{t}&= \begin{pmatrix}
  y_{\text{Total},t}\\
  y_{A,t}\\
  y_{B,t}\\
  y_{C,t}
  \end{pmatrix}  \\
  &= {\color{blue}\underbrace{\begin{pmatrix}
                1 & 1 & 1 \\
                1 & 0 & 0 \\
                0 & 1 & 0\\
                0 & 0 & 1
                \end{pmatrix}}_{\bS}}
     {\color{red}\underbrace{\begin{pmatrix}
       y_{A,t}\\y_{B,t}\\y_{C,t}
       \end{pmatrix}}_{\bm{b}_{t}}}
\end{align*}
\end{textblock}


## Forecast reconciliation

\alert{What we want}

* Forecasts of all series at all levels of aggregation.

\alert{Solution}

* We model and forecast all series independently.
* We "reconcile" the forecasts to make them coherent.


## The coherent subspace

\begin{textblock}{9}(.2,1)\fontsize{13}{13}\sf
\begin{block}{Coherent subspace}
$n_b$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{\chi}^n$ for which linear constraints hold for all $\bm{y}\in\mathfrak{s}$.
\end{block}\vspace*{-0.3cm}
\begin{block}{Hierarchical time series}
An $n$-dimensional multivariate time series such that $\bm{y}_t\in\mathfrak{s}\quad\forall t$.
\end{block}\vspace*{-0.3cm}
\begin{block}{Coherent point forecasts}
$\tilde{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\tilde{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
\end{block}\vspace*{-0.2cm}
\end{textblock}
\only<2-3>{\begin{textblock}{7.5}(.2,6.75)\fontsize{13}{13}\sf
\begin{alertblock}{Base forecasts}
Let $\hat{\bm{y}}_{t+h|t}$ be vector of \emph{incoherent} initial $h$-step forecasts.$\phantom{y_{t|h}}$
\end{alertblock}
\end{textblock}}
\only<3>{\begin{textblock}{7.5}(8.3,6.75)\fontsize{13}{13}\sf
\begin{alertblock}{Reconciled forecasts}
Let $\bm{M}$ be a projection matrix. $\tilde{\bm{y}}_{t+h|t}=\bm{M}\hat{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$.
\end{alertblock}
\end{textblock}}

\placefig{9.4}{.0}{width=6.6cm}{3D_hierarchy}
\begin{textblock}{3}(11.4,5.6)\fontsize{13}{13}\sf
\begin{block}{}
\centerline{$y_{Tot} = y_A + y_B$}
\end{block}
\end{textblock}

## Linear projection reconciliation
\fontsize{14}{16}\sf
\vspace*{0.2cm}\begin{alertblock}{}
\centerline{$\tilde{\bm{y}}_{t+h|t}= \bm{M}\hat{\bm{y}}_{t+h|t}$}
\end{alertblock}\vspace*{-0.2cm}

* If $\bm{S}$ forms a basis set for $\mathfrak{s}$, then projections are of the form $\bm{M} = \bS(\bS'\bm{\Psi}\bS)^{-1}\bS'\bm{\Psi}$ where $\bm{\Psi}$ is a positive definite matrix.
* Coherent base forecasts are unchanged since $\bm{M}\hat{\bm{y}}=\hat{\bm{y}}$
* If $\hat{\bm{y}}$ is unbiased, then $\tilde{\bm{y}}$ is also unbiased.
* $\bm{W}_h = \var[\by_{T+h} - \hat{\by}_{T+h|T} \mid \by_1,\dots,\by_T]$ is the covariance matrix of the base forecast errors.
* $\bm{V}_h = \var[\by_{T+h} - \tilde{\by}_{T+h|T}  \mid \by_1,\dots,\by_T])  = \bm{M}\bm{W}_h\bm{M}'$ is the covariance matrix of the reconciled forecast errors.
* How to choose the best $\bm{\Psi}$?

\vspace*{10cm}

## Minimum trace reconciliation

\begin{textblock}{6.4}(9,-0.1)\begin{block}{}
Wickramasuriya et al (2019)
\end{block}\end{textblock}

\vspace*{0.2cm}\begin{alertblock}{Minimum trace (MinT) reconciliation}
If $\bm{M}$ is a projection, then trace of $\bm{V}_h$ is minimized when $\bm{\Psi} = \bm{W}_h$, so that
\centerline{$\bm{M} = \bS(\bS'\bm{W}_h^{-1}\bS)^{-1}\bS'\bm{W}_h^{-1}$}
\end{alertblock}
\begin{block}{}
\centerline{$\displaystyle\textcolor{red}{\tilde{\by}_{T+h|T}}
= \bm{M} ~ \textcolor{blue}{\hat{\by}_{T+h|T}}$}
\end{block}\vspace*{-0.2cm}
\centerline{\hspace*{1.4cm}\textcolor{red}{Reconciled forecasts}\hfill\textcolor{blue}{Base forecasts}\hspace*{2.9cm}}\vspace*{-0.2cm}

* Trace of $\bm{V}_h$ is sum of forecast variances.
* MinT is $L_2$ optimal amongst linear unbiased forecasts.
* How to estimate $\bm{W}_h = \var[\by_{T+h} - \hat{\by}_{T+h|T} \mid \by_1,\dots,\by_T]$?

## Linear projections

\begin{textblock}{5}(7,-0.2)
\begin{block}{}
\centerline{$\tilde{\by}_{T+h|T}=\bm{M}\hat{\by}_{T+h|T}$}
\end{block}
\end{textblock}

\begin{textblock}{9.4}(.5,1.2)
\begin{alertblock}{Reconciliation method \hspace*{0.5cm} $\bm{M}$}
\begin{tabular}{l@{\hspace*{-0.5cm}}l}
  OLS             & $\bS(\bS'\bS)^{-1}\bS'$ \\
  WLS(var)        & $\bS(\bS'\bm{\Lambda}_v\bS)^{-1}\bS'\bm{\Lambda}_v$ \\
  WLS(struct)     & $\bS(\bS'\bm{\Lambda}_s\bS)^{-1}\bS'\bm{\Lambda}_s$ \\
  MinT(sample)    & $\bS(\bS'\hat{\bm{W}}_{\text{sam}}^{-1}\bS)^{-1}\bS' \hat{\bm{W}}_{\text{sam}}^{-1}$  \\
  MinT(shrink)\hspace*{2cm}    & $(\bS'\hat{\bm{W}}_{\text{shr}}^{-1}\bS)^{-1}\bS' \hat{\bm{W}}_{\text{shr}}^{-1}$  \\
\end{tabular}
\end{alertblock}
\end{textblock}
\begin{textblock}{15}(.2,5.7)\fontsize{13}{15}\sf
\begin{itemize}\parskip=0cm
\item $\bm{\Lambda}_v = \text{diag}(\bm{W}_1)^{-1}$
\item $\hat{\bm{W}}_{\text{sam}}$ is sample estimate of the residual covariance matrix
\item $\hat{\bm{W}}_{\text{shr}}$ is shrinkage estimator $\tau \text{diag}(\hat{\bm{W}}_{\text{sam}})+(1-\tau)\hat{\bm{W}}_{\text{sam}}$\\ where $\tau$ selected optimally.
\item Still need a good estimate of $\bm{W}_h$ for forecast variance.
\end{itemize}
\end{textblock}
\begin{textblock}{14}(4.5,5.7)\fontsize{13}{15}\sf
\begin{itemize}\tightlist
\item $\bm{\Lambda}_s = \text{diag}(\bS\bm{1})^{-1}$
\end{itemize}
\end{textblock}
\begin{textblock}{5}(10.3,3.35)
\begin{block}{}
These approximate MinT by assuming $\bm{W}_h = k_h \bm{W}_1$.
\end{block}
\end{textblock}

## Key papers
\fontsize{12}{12}\sf\vspace*{-0.15cm}
\begin{itemize}\tightlist
\item \fullcite{hierarchical}
\item \fullcite{fasthts}
\item \fullcite{mint}
\item \fullcite{htsgeometry}
\item \fullcite{Di_FonGir2022b}
\end{itemize}

## Example: Australian tourism
\fontsize{10}{11}\sf

```{r tourismdata00, echo=TRUE}
tourism
```

## Example: Australian tourism
\fontsize{10}{11}\sf

```{r tourismagg, echo=TRUE}
tourism_agg <- tourism |>
  aggregate_key((state/zone/region) * purpose, visitors = sum(visitors))
```

```{r tourismagg2, echo=FALSE}
tourism_agg
```

## Example: Australian tourism
\fontsize{10}{11}\sf

```{r tourismmodels, echo=TRUE}
#| dependson: tourismagg
fit <- tourism_agg |>
  filter(year(month) <= 2015) |>
  model(ets = ETS(visitors))
```

```{r tourismmodels1, echo=FALSE}
fit
```

## Example: Australian tourism
\fontsize{10}{11}\sf

```{r fctourism, echo=TRUE}
#| dependson: tourismmodels
fc <- fit |>
  reconcile(mint_s = min_trace(ets, method = "mint_shrink")) |>
  forecast(h = "2 years")
```

```{r fctourism1, echo=FALSE}
#| dependson: fctourism
fc
```

## Example: Australian tourism
\fontsize{9}{10}\sf

```{r fcaccuracy2, echo=TRUE}
#| dependson: fctourism
fc |>
  accuracy(tourism_agg, measures = list(mase = MASE, rmsse = RMSSE)) |>
  group_by(.model) |>
  summarise(mase = mean(mase), rmsse = sqrt(mean(rmsse^2))) |>
  arrange(rmsse)
```

\only<2>{\begin{textblock}{7}(7,4)
\begin{block}{}\fontsize{13}{14}\sf
\begin{itemize}\tightlist
\item Overall, MinT reconciliation forecasts are better than the base ETS forecasts.
\end{itemize}
\end{block}
\end{textblock}}

## Example: Australian tourism
\fontsize{9}{10}\sf

```r
fc |>
  accuracy(tourism_agg, measures = list(mase = MASE, rmsse = RMSSE)) |>
  group_by(.model, level) |>
  summarise(mase = mean(mase), rmsse = sqrt(mean(rmsse^2))) |>
  arrange(level, rmsse)
```

\vspace*{-0.3cm}

```{r fcaccuracy3, echo=FALSE}
#| dependson: fctourism
fc |>
  accuracy(tourism_agg,
    measures = list(mase = MASE, rmsse = RMSSE)
  ) |>
  mutate(
    level = case_when(
      is_aggregated(state) & is_aggregated(purpose) ~ "National",
      is_aggregated(zone) & is_aggregated(purpose) & !is_aggregated(state) ~ "State",
      is_aggregated(region) & is_aggregated(purpose) & !is_aggregated(zone) ~ "Zone",
      is_aggregated(purpose) & !is_aggregated(region) ~ "Region",
      !is_aggregated(purpose) & is_aggregated(state) ~ "Purpose",
      TRUE ~ "Other"
    ),
    level = factor(level, levels = c("National", "State", "Zone", "Region", "Purpose", "Other"))
  ) |>
  group_by(.model, level) |>
  summarise(mase = mean(mase), rmsse = sqrt(mean(rmsse^2))) |>
  arrange(level, rmsse) |> 
  filter(level != "Other")
```

\only<2>{\begin{textblock}{7}(7,4)
\begin{block}{}\fontsize{13}{14}\sf
\begin{itemize}\tightlist
\item Overall, MinT reconciliation forecasts are better than the base ETS forecasts.
\item MinT reconciliation forecasts are better than the base ETS forecasts at all levels except national.
\end{itemize}
\end{block}
\end{textblock}}

# Probabilistic forecast reconciliation

## Coherent probabilistic forecasts
\begin{textblock}{9.5}(0.2,1)\fontsize{13}{14}\sf
\begin{block}{Coherent probabilistic forecasts}
A probability triple $(\mathfrak{s}, \mathscr{F}_{\mathfrak{s}}, \breve{\nu})$ is coherent with the bottom probability triple $(\mathbb{\chi}^m, \mathscr{F}_{\mathbb{\chi}^m}, \nu)$, if
\centerline{$\breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{\chi}^m}$}
\end{block}\vspace*{-0.2cm}
\begin{itemize}\tightlist
\item Random draws from coherent distribution must lie on $\mathfrak{s}$.
\item The probability of points not on $\mathfrak{s}$ is zero.
\item The reconciled distribution is a transformation of the base forecast distribution that is coherent on $\mathfrak{s}$.
\end{itemize}
\end{textblock}
\begin{textblock}{7}(9.5,1.2)
\resizebox{\textwidth}{!}{
\input figs/probforerec_schematic.tex
}
\end{textblock}
\begin{textblock}{7}(9.5,7.5)
\centerline{$\psi = s \circ g$}
\end{textblock}

## Simulation from a reconciled distribution

\begin{block}{}
Suppose that $\left(\hat{\bm{y}}^{[1]},\ldots,\hat{\bm{y}}^{[L]}\right)$ is a sample drawn from an incoherent probability measure $\hat{\nu}$. Then $\left(\tilde{\bm{y}}^{[1]},\ldots,\tilde{\bm{y}}^{[L]}\right)$ where $\tilde{\bm{y}}^{[\ell]}:=\psi(\hat{\bm{y}}^{[\ell]})$ for $\ell=1,\ldots,L$, is a sample drawn from the reconciled probability measure $\tilde{\nu}$.
\end{block}\vspace*{-0.4cm}

* Simulate future sample paths for each series, by simulating from each model using a multivariate bootstrap of the residuals (to preserve cross-correlations).
* Reconcile the sample paths.
* The reconciled sample paths are a sample from the reconciled distribution.

## Simulation from a reconciled distribution

```{r}
#| label: sim_bootstrap
#| include: false
p <- tidyr::expand_grid(
    time = seq(100),
    series = seq(20)
  ) |>
  mutate(res = rnorm(n())) |>
  ggplot(aes(x=time, y=series, fill=res)) +
  geom_tile() +
  scale_y_continuous(breaks = seq(20), minor_breaks = NULL, expand=c(0,0)) +
  guides(fill = "none")
Cairo::CairoPDF(file="figs/sim_bootstrap.pdf", width=8, height=4)
  print(p)
crop::dev.off.crop()
slices <- sample(seq(100), replace = TRUE, size = 20)
for(i in seq_along(slices)) {
  Cairo::CairoPDF(file=paste0("figs/sim_bootstrap_", i, ".pdf"), width=8, height=4)
    print(p +
      geom_rect(aes(xmin = slices[i], xmax = slices[i]+0.9, ymin = 0.5, ymax = 20.5),
                 fill = "transparent", col="white"))
  crop::dev.off.crop()
}
```

\vspace*{0.2cm}
\centerline{\includegraphics[width=15.5cm]{figs/sim_bootstrap.pdf}}

## Simulation from a reconciled distribution

\vspace*{0.2cm}
\centerline{
\animategraphics[loop,autoplay,width=15.5cm]{10}{figs/sim_bootstrap_}{1}{20}
}

## Key papers

* \fullcite{coherentprob}
* \fullcite{CorEtAl2022}


# Cross-temporal probabilistic forecast reconciliation

## Temporal aggregations

\only<1>{\placefig{0.1}{1.3}{width=15.8cm}{tourism7}}
\only<2>{\placefig{0.1}{1.3}{width=15.8cm}{tourism8}}

## Temporal aggregations: monthly data

\only<1>{\begin{tikzpicture}
  \tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
  \tikzstyle[level distance=.1cm]
  \tikzstyle[sibling distance=7cm]
  \tikzstyle{level 1}=[sibling distance=72mm,set style={{every node}+=[fill=blue!15]}]
  \tikzstyle{level 2}=[sibling distance=36mm,set style={{every node}+=[fill=yellow]}]
  \tikzstyle{level 3}=[sibling distance=12mm,font=\scriptsize,set style={{every node}+=[fill=green]}]
  \node{Annual}[edge from parent fork down]
  child {node {Semi-Annual$_1$}
      child {node {Q$_1$}
          child {node {\scriptsize M$_1$}}
          child {node {\scriptsize M$_2$}}
          child {node {\scriptsize M$_3$}}
        }
      child {node {Q$_2$}
          child {node {\scriptsize M$_4$}}
          child {node {\scriptsize M$_5$}}
          child {node {\scriptsize M$_6$}}
        }
    }
  child {node {Semi-Annual$_2$}
      child {node {Q$_3$}
          child {node {\scriptsize M$_7$}}
          child {node {\scriptsize M$_8$}}
          child {node {\scriptsize M$_9$}}
        }
      child {node {Q$_4$}
          child {node {\scriptsize M$_{10}$}}
          child {node {\scriptsize M$_{11}$}}
          child {node {\scriptsize M$_{12}$}}
        }
    };
\end{tikzpicture}}
\only<2->{\begin{tikzpicture}
  \tikzstyle{every node}=[ellipse,draw,inner sep=0.2pt,fill=red!15,font=\small]
  \tikzstyle[level distance=.1cm]
  \tikzstyle[sibling distance=7cm]
  \tikzstyle{level 1}=[sibling distance=48mm,set style={{every node}+=[fill=blue!15]}]
  \tikzstyle{level 2}=[sibling distance=24mm,set style={{every node}+=[fill=yellow]}]
  \tikzstyle{level 3}=[sibling distance=12mm,set style={{every node}+=[fill=green]}]
  \node{Annual}[edge from parent fork down]
  child {node {FourM$_1$}
      child {node {BiM$_1$}
          child {node {\scriptsize M$_1$}}
          child {node {\scriptsize M$_2$}}
        }
      child {node {BiM$_2$}
          child {node {\scriptsize M$_3$}}
          child {node {\scriptsize M$_4$}}
        }
    }
  child {node {FourM$_2$}
      child {node {BiM$_3$}
          child {node {\scriptsize M$_5$}}
          child {node {\scriptsize M$_6$}}
        }
      child {node {BiM$_4$}
          child {node {\scriptsize M$_7$}}
          child {node {\scriptsize M$_8$}}
        }
    }
  child {node {FourM$_3$}
      child {node {BiM$_5$}
          child {node {\scriptsize M$_9$}}
          child {node {\scriptsize M$_{10}$}}
        }
      child {node {BiM$_6$}
          child {node {\scriptsize M$_{11}$}}
          child {node {\scriptsize M$_{12}$}}
        }
    };
\end{tikzpicture}}\pause

## Monthly Australian Tourism Demand

\begin{textblock}{6}(0.2,1.2)
\centering\fontsize{12}{13}\sf
\textbf{Geographical division}\\
\includegraphics[width = 5.5cm, trim= 0 0 180 0, clip=true]{aus_map}\\[-0.4cm]
\faTimes\\
\textbf{Purpose of travel}\\
{\fontsize{11}{12}\sf Holiday, Visiting friends \& relatives, Business, Other}
\end{textblock}

\begin{textblock}{10}(6.1,1)
\fontsize{11}{14}\sf\tabcolsep=0.12cm
\begin{itemize}
\item \textbf{Grouped ts}\newline (geographical divisions $\times$ purpose of travel)

\begin{tabular}{lccccc}
\toprule
  & \textbf{AUS} & \textbf{States} & \textbf{Zones$^\ast$} & \textbf{Regions} & \textbf{Tot}\\
  \midrule
  \textbf{geographical} & {\color{newblue}1} & {\color{newblue}7} & {\color{newblue}21} & {\color{newblue}76} & 105 \\
  \textbf{purpose} & {\color{newblue}4} & {\color{newblue}28} & {\color{newblue}84} & {\color{avocado}304} & 420\\
  \midrule
  \textbf{total} & 5 & 35 & 105 & 380 & \textbf{525}\\
  \bottomrule
\end{tabular}
\centerline{{\color{newblue}$n_a = 221$}, {\color{avocado}$n_b = 304$}, and $\textbf{n = 525}$}

\item \textbf{Temporal framework}, frequencies:\\[0.2cm]
\begin{multicols}{2}
  \begin{itemize}\tightlist
  \item Monthly
  \item Bi-Monthly
  \item Quarterly
  \end{itemize}
  \begin{itemize}\tightlist
  \item Four-Monthly
  \item Semi-Annual
  \item Annual
  \end{itemize}
\end{multicols}
\end{itemize}
\end{textblock}

## Monthly Australian Tourism Demand

* Monthly data: January 1998 to December 2016

* Time series cross-validation; initial training set 10 years.

* One-month increase in each training set

* For each training set, compute temporally aggregated series for $k \in \{1,2,3,4,6,12\}$, and produce forecasts up to $h_2=6$, $h_3=4$, $h_4=3$, $h_6=2$ and $h_{12}=1$ steps ahead.

* Automatic ETS forecasts on log-transformed data

## Monthly Australian Tourism Demand

\alert{Reconciliation approaches}\fontsize{13}{14}\sf

* Cross-temporal \textbf{\color{newblue}{bottom-up}} and \textbf{\color{newblue}{partly bottom-up}}

  \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
  ct$(bu)$ & ct$(shr_{cs}, bu_{te})$ & ct$(wlsv_{te}, bu_{cs})$
  \end{tabular}

* Optimal forecast reconciliation with \textbf{\color{newblue}{one-step residuals}}

    \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
    oct$(ols)$ & oct$(struc)$ & oct$(wlsv)$ & oct$(bdshr)$
    \end{tabular}

* Optimal forecast reconciliation with \textbf{\color{newblue}{multi-step residuals}}

    \begin{tabular}{M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}|M{0.24\linewidth}}
    oct$_h(hbshr)$ & oct$_h(bshr)$ & oct$_h(hshr)$ & oct$_h(shr)$
    \end{tabular}

## Monthly Australian tourism data -- CRPS skill scores
\fontsize{12}{13}\sf\vspace*{0.2cm}

\centerline{\textcolor{red}{Worse than benchmark}\qquad \textbf{Best}}

\centering
\footnotesize
\begin{tabular}[t]{lrr}
& \textbf{$\forall k \in \{12,6,4,3,2,1\}$} & \textbf{$k = 1$}\\
\midrule
base                      & \cellcolor{LightOrange!30} {1.000}  & \cellcolor{LightOrange!30} {1.000} \\
ct$(bu)$                  & \textcolor{red}{1.321}              & \textcolor{red}{1.077} \\
ct$(shr_{cs}, bu_{te})$   & \textcolor{red}{1.057}              & {0.976} \\
ct$(wlsv_{te}, bu_{cs})$  & \textcolor{red}{1.062}              & {0.976}\\
oct$(ols)$                & {0.989}                             & {0.982}\\
oct$(struc)$              & {0.982}                             & {0.970}\\
oct$(wlsv)$               & {0.987}                             & {0.952} \\
oct$(bdshr)$              & {0.975}                             & {\textbf{0.949}} \\
oct$_h(hbshr)$            & {0.989}                             & {0.982} \\
oct$_h(bshr)$             & {0.994}                             & {0.988}\\
oct$_h(hshr)$             & {\textbf{0.969}}                    & {0.953}\\
oct$_h(shr)$              & \textcolor{red}{1.007}              & \textcolor{red}{1.000}
\end{tabular}

## Key papers
\fontsize{13}{15}\sf

* \fullcite{temporal-hierarchies}
* \fullcite{Di_FonGir2022a}
* \fullcite{ctprob}

## Software
\fontsize{11}{12}\sf\vspace*{0.3cm}

\hspace*{-0.6cm}\begin{tabular}{llP{1.7cm}cP{1.7cm}c}
\toprule
Package                                                                      & Language  & Cross-sectional  & Temporal    & Cross-temporal  & Probabilistic\\
\midrule
\texttt{\href{https://pkg.earo.me/hts/}{hts}}
    & R         & \checkmark       &             &                 & \\
\texttt{\href{http://pkg.robjhyndman.com/thief/}{thief}}
    & R         &                  & \checkmark  &                 & \\
\texttt{\href{https://fable.tidyverts.org}{fable}}
    & R         & \checkmark       &             &                 & \checkmark\\
\texttt{\href{https://danigiro.github.io/FoReco/}{FoReco}}
    & R         & \checkmark       & \checkmark  & \checkmark      & \checkmark\\
\texttt{\href{https://angelpone.github.io/pyhts/}{pyhts}}
    & Python    & \checkmark       & \checkmark  &                 & \\
\texttt{\href{https://nixtla.github.io/hierarchicalforecast/}{hierarchicalforecast}}
    & Python    & \checkmark       &             &                 & \checkmark \\
\bottomrule
\end{tabular}

* `hts`, `thief`, and `FoReco` use `ts` objects
* `fable` uses `tsibble` objects
* `fable` has plans to implement temporal and cross-temporal reconciliation

## More information
\fontsize{18}{20}\sf

\href{https://robjhyndman.com/frreview}{\faicon{newspaper} robjhyndman.com/frreview}

\href{https://robjhyndman.com/seminars/fr_overview.html}{\faicon{display} robjhyndman.com/frslides}

\href{https://aus.social/@robjhyndman}{\includegraphics[width=0.5cm]{figs/mastodon}\, aus.social/@robjhyndman}

\href{https://github.com/robjhyndman}{\faicon{github}  @robjhyndman}

\href{mailto:rob.hyndman@monash.edu}{\faicon{envelope}  rob.hyndman@monash.edu}

\nocite{hierarchical,fasthts, mint, hfreview, htsgeometry}
\nocite{Di_FonGir2022a,temporal-hierarchies,ctprob}
